Reviving stochasticity: SMBH-binary eccentricity is inherently random

### 2023-06-21 papers/paper-eccentricity/paper-eccentricity.tex
Initial check of Sec 3.1. Final check to be done when the new plots are in place.

\begin{figure*}
    \centering
    \includegraphics{eccentricities.pdf}
    \caption{Eccentricity $e$ (note the non-linear scale) as a function of shifted time $t'=t-t_\mathrm{bound}$ for the highest mass resolution simulations from the $e_0 = 0.90$ set (blue lines) and $e_0 = 0.99$ set (orange lines). 
    The downwards-pointing arrows indicate the median time when the SMBH binaries becomes hard for the two simulation sets. 
    In both the shown $e_0 = 0.90$ and $e_0 = 0.99$ sets, one simulation has a comparatively low eccentricity, displacing it to a value of $e$ greater than $2.5\sigma$ from the collective mean. 
    In the $e_0=0.90$ set, seven simulations have a SMBH binary merger within $50\,\mathrm{Myr}$, as indicated by the rapid circularisation of the eccentricity.}
    \label{fig:eccentricities}
\end{figure*}

@@

The SMBH binary eccentricity for both the $e_0=0.90$ (blue) and $e_0=0.99$ (orange) orbits are shown in \autoref{fig:eccentricities} as a function of shifted time $t' = t - t_\mathrm{bound}$ for the highest mass resolution sets. 
At least one simulation is seen to lie significantly beyond the mean eccentricity in each set, with $e_\mathrm{h} \sim 0.8$ for the $e_0=0.90$ set and $e_\mathrm{h}\sim 0.2$ for the $e_0=0.99$ set. 
The median time when each simulation set forms a hard binary is similar between the two sets, as indicated by the arrows in \autoref{fig:eccentricities}.
The $e_0=0.90$ set also demonstrates seven SMBH-binary mergers within $50\,\mathrm{Myr}$ of forming a bound binary, seen as a rapid circularisation in eccentricity in \autoref{fig:eccentricities}, which is captured self-consistently using \ketju{}.

To characterise the scatter in eccentricity, we determine the mean eccentricity $e_\mathrm{h}$ over five orbital periods centred on the orbit within which the SMBH binary has become hard.
The binary hardening radius $a_\mathrm{h}$ is defined as \citep[e.g.][]{merritt2006}
\begin{equation}\label{eq:ahard}
    a_\mathrm{h} = \frac{q}{(1+q)^2} \frac{r_\mathrm{m}}{4} = \frac{r_\mathrm{m}}{16},
\end{equation}
where $r_\mathrm{m}=r(m<2M_{\bullet,1})$ is the influence radius and $q$ is the mass ratio between the SMBHs (for our simulations $q=1.0$, giving rise to the second equality in \autoref{eq:ahard}).
Assuming the distribution of mean hard-binary eccentricities is Gaussian, we characterise the inter-simulation eccentricity scatter as the standard deviation in mean values of $e_\mathrm{h}$, denoted as $\sigma_e$.

@@

\begin{figure*}
    \centering
    \includegraphics{orbit}
    \caption{Orbits from $t=0\,\mathrm{Myr}$ to a time shortly after $t_\mathrm{bound}$ of a single SMBH in two representative realisations of the $e_0=0.90$ mergers (left) and the $e_0=0.99$ mergers (right), which by symmetry of the equal mass system is a reflection of the second BH orbit about the $x=-z$ line. 
    Each line is coloured according to the shifted time $t'=t-t_\mathrm{bound}$ of the simulation, however the colours for $|t'|>2\,\mathrm{Myr}$ is constant for visual clarity of the deflection-phase of the evolution. 
    In each inset panel, point A shows a time just before the first hard scattering $\theta_\mathrm{defl}$, and point B a time just after. 
    The circle marker indicates the position of the SMBH just before the SMBHs form a bound binary.}
    \label{fig:orbit}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics{eccentricities.pdf}
    \caption{Eccentricity $e$ (note the non-linear scale) as a function of shifted time $t'=t-t_\mathrm{bound}$ for the highest mass resolution simulations from the $e_0 = 0.90$ set (blue lines) and $e_0 = 0.99$ set (orange lines). 
    The downwards-pointing arrows indicate the median time when the SMBH binaries becomes hard. 
    In both the shown $e_0 = 0.90$ and $e_0 = 0.99$ sets, one simulation has a comparatively low eccentricity, displacing it to a value of $e$ greater than $2.5\sigma$ from the collective mean. 
    In the $e_0=0.90$ set, seven simulations have a SMBH binary merger within $50\,\mathrm{Myr}$, as indicated by the rapid circularisation of the eccentricity.}
    \label{fig:eccentricities}
\end{figure*}

@@

The SMBH binary eccentricity for both the $e_0=0.90$ (blue) and $e_0=0.99$ (orange) orbits are shown in \autoref{fig:eccentricities} as a function of shifted time $t' = t - t_\mathrm{bound}$ for the highest mass resolution sets, where $t_\mathrm{bound}$ is the time when the SMBH binaries become bound. 
At least one simulation is seen to lie significantly beyond the mean eccentricity in each set, with $e_\mathrm{h} \sim 0.8$ for the $e_0=0.90$ set and $e_\mathrm{h}\sim 0.2$ for the $e_0=0.99$ set. 
The median time when each simulation set forms a hard binary is similar between the two sets, as indicated by the arrows in \autoref{fig:eccentricities}.
The $e_0=0.90$ set also demonstrates seven SMBH-binary mergers within $50\,\mathrm{Myr}$ of forming a bound binary, seen as a rapid circularisation in eccentricity in \autoref{fig:eccentricities}, which is captured self-consistently using \ketju{}.

To characterise the scatter in eccentricity, we determine the mean eccentricity $e_\mathrm{h}$ over five orbital periods centred on the orbit within which the SMBH binary has become hard.
The binary hardening radius $a_\mathrm{h}$ is defined as \citep[e.g.][]{merritt2006}
\begin{equation}\label{eq:ahard}
    a_\mathrm{h} = \frac{q}{(1+q)^2} \frac{r_\mathrm{m}}{4} = \frac{r_\mathrm{m}}{16},
\end{equation}
where $r_\mathrm{m}=r(m<2M_{\bullet,1})$ is the influence radius and $q$ is the mass ratio between the SMBHs (for our simulations $q=1.0$, giving rise to the second equality in \autoref{eq:ahard}).
% Assuming the distribution of mean hard-binary eccentricities is Gaussian,
We characterise the inter-simulation eccentricity scatter in the mean values of $e_\mathrm{h}$ with the standard deviation, denoted as $\sigma_e$.

@@

\begin{figure*}
    \centering
    \includegraphics{orbit}
    \caption{Orbits from $t=0\,\mathrm{Myr}$ to a time shortly after $t_\mathrm{bound}$ of a single SMBH in two representative realisations of the $e_0=0.90$ mergers (left) and the $e_0=0.99$ mergers (right), which by symmetry of the equal mass system is a reflection of the second BH orbit about the $x=-z$ line. 
    Each line is coloured according to the shifted time $t'=t-t_\mathrm{bound}$ of the simulation, however the colours for $|t'|>2\,\mathrm{Myr}$ is constant for visual clarity. % of the deflection-phase of the evolution. 
    In each inset panel, point A shows a time just before the first hard scattering $\theta_\mathrm{defl}$, and point B a time just after. 
    The circle marker indicates the position of the SMBH just before the SMBHs form a bound binary.}
    \label{fig:orbit}
\end{figure*}
